Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2020-12-28 RR_manuscript/Draft_RR.tex
edit RR Step 4

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Analytical choices for analyzing multidimensional behavior - many analyst test hypotheses about human speech.},
  pdfauthor={First Author\#, Second Author\#, \ldots\#, \& Last Author\#},
  pdflang={en-EN},
  pdfkeywords={crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis (e.g.~Box 1976, Tukey 1977, de Groot 2014).
They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted (Simmons et al.~2011).
Recent projects have shown that the variability between different data analysts is vast.
This variability can lead independent researchers to draw vastly different conclusions about the same data set (e.g.~Silberzahn et al.~2018, Starns et al.~2019, Botvinik-Nezer et al., 2020).
These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference of data sets.
Human behavior is complex and offers many ways to be translated into numbers.
This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data.
In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it.
This is not trivial given the temporal extension of the acoustic signal and its complex structural composition.
Not only can decisions about measuring the signal influence downstream decisions about statistical modelling, but statistical results or modelling issues can also lead researchers to go back and revise earlier decisions about the measuring process itself.

In this article, we investigate the variability in analytic choices when many analyst teams analyze the same speech production data, a process that involves both decisions regarding the operationalization of a complex observed signal and decisions regarding the statistical modelling.
Specifically, we report the impact of the analytic pipeline on research results obtained by XX teams who gained access to the same set of acoustic recordings in order to answer the same research question.

@@

In a collaborative effort, Silberzahn et al.~(2018) let twenty-nine independent analysis teams address the same research hypothesis
Analytic approaches and consequently the results varied widely between teams.
Sixty-nine percent of the teams found support for the hypothesis, and 31\% did not.
Out of the 29 analytical strategies, there were 21 unique combinations of covariates.
Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses.
The authors results suggest that analytic plurality is a fact of life and not driven by different levels of expertise or bias.
Similar crowd-sourced studies recruiting independent analyst teams showed similar results.

SUM UP:
Neuroscience
Cognitive Modelling
Clinical
Predictive models

While these projects show a large degree of analytical flexibility with impactful consequences, they dealt with flexibility in inferential or computational modelling.
In these studies the data sets were fixed and data collection or measurement could not be changed.

However, in many fields the primary raw data are complex signals that need to be operationalized according to the research question.
In social sciences, the raw observations correspond to human behavior, sometimes measured as a complex visual or acoustic signal.
\textless\textless\textless\textless\textless\textless\textless{} HEAD
Decisions about how to measure a theoretically construct related to that behavior or the underlying cognitive processes might interact with downstream decisions about statistical modelling and vice verse.
=======
Decisions about how to measure a theoretically construct related to that behavior or the underlying cognitive processes might interact with downstream decisions about statistical modelling and vice verse.
\textgreater\textgreater\textgreater\textgreater\textgreater\textgreater\textgreater{} 4860d0ed0c2fc204883e1c150efb5749b4ef1669

To understand how analytical flexibility manifests itself in a scenario where a complex decisions procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set

@@

Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances.
Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g.~Niebuhr et al., 2011).
The latter can also be expressed by global vs local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g.~van Heuven \& van Zanten 2005).
Extra- and para-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain features, such as voice quality, speech rate, and rhythm (REFs).

When testing hypotheses on speech production data, researchers are faced with many choices and possibilities.
The larger the functional domain (e.g.~segments vs words vs utterances), the higher the number of conceivable operationalizations.
These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis (e.g.~Wicherts et al.). Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models.
The present paper probes this garden of forking path in speech analysis. To probe the variability in data analysis pipelines across independent researchers, we provided analytical teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.

@@

Th initiating authors (SC, JC, TR) will conduct the analyses outlined in this section.
We will describe the variation in model specifications in several ways:

First, we will calculate summary statistics describing variation among analysis, including the nature and number of acoustic measures (e.g.~f0 or duration), the operationalization and the temporal domain of measurement (e.g.~mean of an interval or value at specified point in time), the nature and number of model parameters for both fixed and random effects {[}if applicable{]}, the nature an reasoning behind inferential assessments (e.g.~dichotomous decision based on p-values, ordinal decision based on Bayes factor), as well as the mean, standard deviation and range of effect sizes reported.
We anticipate that the majority of statistical analyses will be expressible as a (generalized) linear regression model.

ADD FORMULA

Since teams will likely use outcome variable that substantially differ in their scales, we will standardize all reported effects by refitting all models with scaled outcome variables (the observed values subtracted from the mean divided by the standard deviation).

We will summarize the variability in standardized effect sizes and predicted values of dependent variables among the individual analyses using standard random effects meta-analytic techniques.
First, we will derive standardized effect sizes from each individual analysis.
Since we anticipate that researchers use multi-level linear regression models, common effect size measures such as Cohen's d are inappropriate.
Effect sizes will be defined as the estimate(s) of the critical predictor(s) (i.e.~critical according to the analysis teams' self-reported inferential criteria) divided by the standard error for the estimate(s).

Upon extracting the standardized effect sizes and standard errors for each analysis, the initiating authors will then fit a cross-classified Bayesian meta-analysis on the analyst team data using the multilevel regression model described below:

\[
\begin{aligned}
\delta_t & \sim \text{Normal}(\theta_i, \sigma_i = \text{se}_i) \\
\theta_i     & \sim \text{Normal} (\mu, \tau) \\
\mu          & \sim \text{Normal} (0, 1) \\
\tau         & \sim \text{HalfCauchy} (0, 1)
\end{aligned}
\]

Effect size (\(\delta_{t}\)) will be the outcome variable.
The likelihood of the outcome variable is assumed to be normally distributed.
Analysis teams will be included as a group-level effect (i.e., random effect).
For all population-level parameters, the model will include regularizing, weakly informative priors (Gelman, 2017), which are normally distributed and centered at 0 with a standard deviation of 1.

A cauchy prior set at 0 with scale 1 will be used for \(\tau\).
We will fit the model with 4000 iterations (2000 warm-up) and Hamiltonian Monte-Carlo sampling of the posterior distribution is carried out using 4 chains distributed across 4 processing cores.
The analysis will be conducted in R (R core team, 2020) and fit using \texttt{stan} (Stan, 2019) via the R package \texttt{brms} (Bürkner, 2019). The code for the model can be found here: INSERT LINK.
We will quantify the extent to which the meta-analytic estimate is modulated by the following main predictors: The peer ratings of each analysis (numeric, 1-100) \ldots{} to be filled.

As a second step, we will explore the extent to which deviations from the meta-analytic mean by individual effect sizes relate to a series of predictors (see below): The deviation score, which serves as the dependent variable in this analysis, will be the

These analyses are secondary to our estimation of variation in effect sizes described above. We wish to quantify relationships among variables, but we have no a priori expectation of effect size and we will not make dichotomous decisions about statistical significance.

The following predictors will be used:

First, we include a measure of the `uniqueness' of individual analyses for
- the set of predictor parameters,
- the set of random effect parameters,
- the acoustic measurement.

The measure of the uniqueness of the set of model parameters is assessed by the Sorensen's Similarity Index (SSI). The SSI is an index typically used in ecology research to compare species composition across sites.
For our purposes, we will treat variables as species and individual analyses as sites.
In order to generate an SSI for each analysis team, we will calculate the average of all pairwise Sorensen's values for all pairs of analyses using the betapart package (Baselga et al.~2018) in R.
We achieve this using the following formula:

\[\beta_{Sorensen} = \frac{(b+c)}{(2a+b+c)}\]

where \(a\) is the number of variables common to both models, \(b\) is the number of variables that occur in the first model but not in the second and \(c\) is the number of variables that occur in the second model but not in the first.

Second, we include a measure of conservativeness of the model specification defined by the number of random effect parameters.

Third, we include the self-proclaimed number of post-hoc changes to teams' acoustic measurements and the self-estimated number of models that they ran prior to settling on their final model.

Forth, we include the major acoustic dimension that has been measured to answer the research question. We will categorize each analysis into the following possible major acoustic dimensions: duration, amplitude, fundamental frequency, spectral properties

Fifth, we include the temporal window that the measurement is taken over defined by the target linguistic unit. We assume the following relevant linguistic units: segment, syllable, word, phrase.

Sixth, we include the following demographic factors about both the analysis teams:
- \ldots{}

DESCRIBE HOW WE WILL LOOK AT THESE THINGS

We will publicly archive all relevant data, code, and materials on the Open Science Framework (ADD LINK).
Archived data will include the original data sets distributed to all analysts, any edited versions of the data analyzed by individual groups, and the data we analyze with our meta-analyses, which include the effect sizes derive from separate analyses, the statistics describing variation in model structure among analyst groups, and the anonymized answers to our surveys of analysts and peer reviewers.
Similarly, we will archive both the analysis code used for each individual analysis and the code from our meta-analyses.
We will also archive copies of our survey instruments from analysts and peer reviewers.

@@

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.},
  pdfauthor={First Author\#, Second Author\#, \ldots\#, \& Last Author\#},
  pdflang={en-EN},
  pdfkeywords={crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

They are a blessing because they afford us the opportunity to look at nature from different angles, which, in turn, allows us to make important discoveries and generate new hypothesis (e.g.~Box 1976, Tukey 1977, de Groot 2014).
They are a curse because idiosyncratic choices can lead to categorically different interpretations, which eventually find their way into the publication record where they are taken for granted (Simmons et al.~2011).
Recent projects have shown that the variability between different data analysts is vast.
This variability can lead independent researchers to draw vastly different conclusions about the same data set (e.g.~Silberzahn et al.~2018, Starns et al.~2019, Botvinik-Nezer et al., 2020).
These projects, however, might still underestimate the extent to which analysts vary because data analysis is not merely restricted to statistical inference of data sets.
Human behavior is complex and offers many ways to be translated into numbers.
This is particularly true for fields that draw conclusions about human behavior and cognition from multidimensional data like audio or video data.
In fields working on human speech production, for example, researchers need to make numerous decisions about what to measure and how to measure it.
This is not trivial given the temporal extension of the acoustic signal and its complex structural composition.
Not only can decisions about measuring the signal influence downstream decisions about statistical modeling, but statistical results or modeling issues can also lead researchers to go back and revise earlier decisions about the measuring process itself.

In this article, we investigate the variability in analytic choices when many analyst teams analyze the same speech production data, a process that involves both decisions regarding the operationalization of a complex observed signal and decisions regarding the statistical modeling.
Specifically, we report the impact of the analytic pipeline on research results obtained by XX teams who gained access to the same set of acoustic recordings in order to answer the same research question.

@@

In a collaborative effort, Silberzahn et al.~(2018) let twenty-nine independent analysis teams address the same research hypothesis.
Analytical approaches and consequently the results varied widely between teams.
Sixty-nine percent of the teams found support for the hypothesis, and 31\% did not.
Out of the 29 analytical strategies, there were 21 unique combinations of covariates.
Importantly, the observed variability was neither predicted by the team's preconceptions about the phenomenon under investigation nor by peer ratings of the quality of their analyses.
The authors results suggest that analytic plurality is a fact of life and not driven by different levels of expertise or bias.
Similar crowd-sourced studies recruiting independent analyst teams showed similar results.

SUM UP:
Neuroscience
Cognitive modeling
Clinical
Predictive models

While these projects show a large degree of analytical flexibility with impactful consequences, they dealt with flexibility in inferential or computational modeling.
In these studies the data sets were fixed and data collection or measurement could not be changed.

However, in many fields the primary raw data are complex signals that need to be operationalized according to the research question.
In social sciences, the raw observations correspond to human behavior, sometimes measured as a complex visual or acoustic signal.
Decisions about how to measure a theoretical construct related to that behavior or its underlying cognitive processes might interact with downstream decisions about statistical modeling and vice versa (Flake \& Fried, 2019).
For example, when working with speech data, a researcher has the option of extracting measurements from a particular point in time within an utterance or from a time interval, depending on which some statistical models will be more useful than others.
In turn, different models will pick up different trends in the data, thus possibly producing diverging or even mutually exclusive results.

To understand how analytical flexibility manifests itself in a scenario where a complex decision procedure is involved in operationalizing and measuring complex signals, the present paper looks at an experimentally elicited speech data set.

@@

Moving onto the expression of higher-level functions like information structure and discourse pragmatics, relevant acoustic cues can be distributed throughout even larger domains, such as phrases and whole utterances.
Differences in position, shape, and alignment of pitch modulations over multiple locations within a sentence are correlated with differences in discourse functions (e.g.~Niebuhr et al., 2011).
The latter can also be expressed by global vs local pitch modulations, as well as acoustic information within the temporal or spectral domain (e.g.~van Heuven \& van Zanten 2005).
Extra- and para-linguistic information, like speaker's intentions, levels of arousal or social identity, are also conveyed by broad-domain features, such as voice quality, rhythm, and intonation (Foulkes \& Docherty, 2006; Ogden, 2004; White, Payne, \& Mattys, 2009).

When testing hypotheses on speech production data, researchers are faced with many choices and possibilities.
The larger the functional domain (e.g.~segments vs words vs utterances), the higher the number of conceivable operationalizations.
These decisions are usually made prior to any statistical analysis, but are at times revised a posteriori (i.e.~after data collection and/or preliminary analyses) in light of unforeseen or surprising outcomes.
These myriads of possible decisions are exponentiated by researcher degrees of freedom related to statistical analysis (e.g.~Wicherts et al.).
Even the analysis of a single measure can be approached via an ever-increasing range of different statistical models.
The present paper probes this garden of forking paths in the analysis of speech.
To assess the variability in data analysis pipelines across independent researchers, we provided the analysis teams with an experimentally elicited speech corpus and asked them to investigate acoustic differences related to a functional contrast that might be manifested across the whole utterance.

@@

Th initiating authors (SC, JC, TR) will conduct the analyses outlined in this section.

\hypertarget{descriptive-statistics}{%
\subsubsection{Descriptive statistics}\label{descriptive-statistics}}

We will calculate summary statistics describing variation among analyses, including the nature and number of acoustic measures (e.g.~f0 or duration), the operationalization and the temporal domain of measurement (e.g.~mean of an interval or value at specified point in time), the nature and number of model parameters for both fixed and random effects {[}if applicable{]}, the nature and reasoning behind inferential assessments (e.g.~dichotomous decision based on p-values, ordinal decision based on Bayes factor), as well as the mean, standard deviation and range of effect sizes reported.
We anticipate that the majority of statistical analyses will be expressible as a (generalized) linear regression model.

FORMULA

\hypertarget{meta-analytical-estimation}{%
\subsubsection{Meta-analytical estimation}\label{meta-analytical-estimation}}

Standard random-effects meta-analytical techniques will be used to summarize the variability in effect sizes and predicted values of dependent variables among the individual analyses.
We anticipate that researchers will use multi-level regression models, so that common effect size measures such as Cohen's \(d\) would be inappropriate.
Since the outcome variables used by the analysis teams might substantially differ in their measurement scales (e.g, Hz for frequency vs ms for duration), we will standardize all reported effects by refitting each model with scaled outcome variables (the observed values subtracted from the mean divided by the standard deviation, i.e.~\emph{z}-scores) using a Bayesian multilevel model.
The standardized effect size (\(\eta_i\)) of each analysis will be the estimated coefficient of the critical predictor (i.e.~critical according to the analysis teams' self-reported inferential criteria).
If multiple predictors within a single analysis have been reported as critical, each will be included in the meta-analytical model (described in details in the next paragraph).
Moreover, to account for the degree of uncertainty around each effect size, which can differ between analyses, we will enter in the meta-analytical model the standard deviation of each effect size returned by each analysis' multilevel model, as the standard error of the effect size (\(\text{se}_i\)).
This will enable us to fit a so-called ``measurement-error'' model, in which standardized effect sizes with smaller standard errors will affect the meta-analytical estimate more than effect sizes with bigger standard errors.

After the extraction of the standardized effect sizes \(\eta_i\) and related standard error \(\text{se}_i\) for each critical predictor of the individual analyses, the initiating authors will then fit a cross-classified Bayesian meta-analysis using the multilevel regression model described below:

\[
\begin{aligned}
\eta_i   & \sim \text{Normal}(\mu_i, \sigma_i) \\
\mu_i     & = \alpha + \alpha_{\text{team}[i]} + \beta_n\\
\alpha  & \sim \text{Normal}(0, 1) \\
\beta_n & \sim \text{Normal}(0, 1) \\
\sigma_{\alpha_{\text{team}}} & \sim \text{HalfCauchy}(0, 1) \\
\sigma_i  & = \text{se}_i
\end{aligned}
\]

The outcome variable will be the set of standardized effect sizes.
The respective standard errors \(\text{se}_i\) will be included to fit a measurement-error model.
The likelihood of \(\eta_i\) is assumed to be normally distributed (Knight 2000).
The analysis teams will be included as a group-level effect (i.e., random effect).
For each population-level parameter \(\beta_n\) (i.e., the fixed effects, see below), the model will include regularizing, weakly informative priors (Gelman, 2017), which are normally distributed and centered at 0 with a standard deviation of 1.
We will fit the model with 4000 iterations (2000 warm-up) and Hamiltonian Monte-Carlo sampling of the posterior distribution is carried out using 4 chains distributed across 4 processing cores.
The analysis will be conducted in R (R core team, 2020) and fit using Stan (Stan Development Team, 2019) via the R package brms (Bürkner, 2019).
The code for the model can be found here: INSERT LINK.

We will quantify the extent to which the standardized effect sizes are modulated by the following population-level predictors:

\begin{itemize}
\tightlist
\item
  The peer ratings of each analysis (numeric, 1-100).
\item
  \ldots{}
\end{itemize}

\hypertarget{exploratory-road-map}{%
\subsubsection{Exploratory road map}\label{exploratory-road-map}}

As a second step, we will explore the extent to which deviations from the meta-analytical mean by individual standardized effect sizes relate to a series of predictors (see below): The deviation score, which serves as the dependent variable in this analysis, will be the difference (\(\delta_i\)) between the meta-analytical mean (\(\hat{\eta}\)) and the individual standardized effect size of each analysis (\(\eta_i\)).
These exploratory analyses are secondary to our estimation of variation in effect sizes described above.
We wish to quantify relationships among variables, but we have no a priori expectation of effect size and we will not make dichotomous decisions about statistical significance.
We will model the effect of the following predictors:

\begin{itemize}
\tightlist
\item
  \emph{Measure of uniqueness} of individual analyses for the set of predictors in each model.
\item
  \emph{Measure of conservativeness} of the model specification.
\item
  \emph{Number of post-hoc changes to the acoustic measurements} the teams will report to have carried out.
\item
  \emph{Number of models} the teams will report to have run.
\item
  \emph{Major dimension} that has been measured to answer the research question.
\item
  \emph{Temporal window} that the measurement is taken over.
\item
  \emph{Demographic factors} of analysis teams and analysts.
\end{itemize}

The measure of uniqueness of predictors will be assessed by the Sørensen-Dice Index (SDI, Dice, 1945; Sørensen, 1948).
The SDI is an index typically used in ecology research to compare species composition across sites.
For our purposes, we will treat predictors as species and individual analyses as sites.
The SDI for a pair of analyses \((X, Y)\) can be obtained using the following formula:

\[\text{SDI} = \frac{2|X \cap Y|}{|X|+|Y|}\]

where \(|X \cap Y|\) is the number of variables common to both models, and \(|X|+|Y|\) is the sum of the number of variables that occur in each model.

In order to generate a unique SDI for each analysis team, we will calculate the average of all pairwise SDIs for all pairs of analyses using the \texttt{beta.pair()} function in the betapart R package (Baselga et al.~2018).
The major measurement dimension of each analysis will be categorized according to the following possible groups: duration, amplitude, fundamental frequency, other spectral properties (e.g.~frequency center of gravity, harmonics difference, etc.), other measures (e.g.~principal components, vowel dispersion, etc.)
The temporal window that the measurement is taken over is defined by the target linguistic unit.
We assume the following relevant linguistic units: segment, syllable, word, phrase.

We will include the following demographic factors about both the analysis teams:

\begin{itemize}
\tightlist
\item
  \ldots{}
\end{itemize}

We will publicly archive all relevant data, code, and materials on the Open Science Framework (\url{https://osf.io/3bmcp/}).
Archived data will include the original data sets distributed to all analysts, any edited versions of the data analyzed by individual groups, and the data we analyze with our meta-analyses, which include the effect sizes derived from separate analyses, the statistics describing variation in model structure among analysis teams, and the anonymized answers to our surveys of analysts and peer reviewers.
Similarly, we will archive both the analysis code used for each individual analysis and the code from our meta-analyses.
We will also archive copies of our survey instruments from analysts and peer reviewers.

@@

\leavevmode\hypertarget{ref-dice1945}{}%
Dice, L. R. (1945). Measures of the amount of ecologic association between species. \emph{Ecology}, \emph{26}(3), 297--302.

\leavevmode\hypertarget{ref-flake2019}{}%
Flake, J. K., \& Fried, E. I. (2019). Measurement schmeasurement: Questionable measurement practices and how to avoid them. Pre-print available at PsyArXiv.

\leavevmode\hypertarget{ref-foulkes2006}{}%
Foulkes, P., \& Docherty, G. (2006). The social life of phonetics and phonology. \emph{Journal of Phonetics}, \emph{34}(4), 409--438.

\leavevmode\hypertarget{ref-ogden2004}{}%
Ogden, R. (2004). Non-modal voice quality and turn-taking in {F}innish. \emph{Sound Patterns in Interaction: Cross-Linguistic Studies from Conversation}, 29--62.

@@

\leavevmode\hypertarget{ref-sorensen1948}{}%
Sørensen, T. (1948). A method of establishing groups of equal amplitude in plant sociology based on similarity of species and its application to analyses of the vegetation on {D}anish commons. \emph{Kongelige Danske Videnskabernes Selskab}, \emph{5}(4), 1--34.

\leavevmode\hypertarget{ref-white2009}{}%
White, L., Payne, E., \& Mattys, S. L. (2009). Rhythmic and prosodic contrast in {V}enetan and {S}icilian {I}talian. In M. Vigario, S. Frota, \& M. J. Freitas (Eds.), \emph{Phonetics and phonology: Interactions and interrelations} (pp. 137--158). Amsterdam: John Benjamins.
